\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\begin{figure}[h]
\makebox[\textwidth]{%
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm.pdf}%
\hfill    
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh.pdf}%
}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}%
}%
\caption{A simple test-case of a square region with four subregions. The permeability contrast is constant. The mesh is unstructured but fixed. After the injection of fluid $1$ at a velocity of u = 1, the velocity magnitude drops to zero. The main finger starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary. The mechanism that still drives the phenomenon is the pressure difference and the tip-splitting pattern can be more profound. }
\label{fig:square}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\subfigure[Initial and boundary conditions]{\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
\caption{This is the first test-case of a square region with four subregions of constant permeabilities K. The mesh is unstructured but fixed and on average there are 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet. This is a cross flow example based on the experimental work of \citet{evans_1994}. The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
\label{fig:square}
\end{center}
\end{figure}
